Hierarchical Inference of the Intrinsic Ellipticity Distribution of Galaxies during Weak Lensing Analysis

### 2013-04-04 docs/ms.tex
Update ms.tex

The accuracy of Weak Lensing survey depends on both galaxy shape measurement
and shear inference .In this paper our main concern is how to infere
shear in a HB method instead off traditional averaging method and
it does not involve the shape measurement part .Therefore we assume
we have perfect galaxies ellipticity measurement,and all the possible
inaccuracy is due to this HB shear inference method.

We calculated the average of $g^{estimated}-g^{true}$ of 10,000 data
sets as described above.Each data set has 64 patches and 8{*}64 galaxies,and
the true P($\epsilon$) is Beta(2.8,2.8) .For both Beta function model
and step funtion model we then determin the best fitted parameters
m and c of fomula (15).Figure 9 shows an example of step funtion model
with prior prefator $\xi=3$.The results of the systematical bias
analysis are tabulated in table 1.

>>>>

To isolate out the source of the bias in this section,we assume we have perfect measurement on galaxy shape.
We will discuss more on the influence of measurement error section 4.4 .

We calculated the average of $g^{estimated}-g^{true}$ of 10,000 data
sets as described in section 4.1 .Each data set has 64 patches and 8$\times$64 galaxies,and
the true P($\epsilon$) is Beta(2.8,2.8).The input true values of $\vec{g}_{1}$ and $\vec{g}_{2}$ of the 
64$\times$10,000 sky patches are generated randomly from a uniform distribution from -0.1 to 0.1 . 
with prior prefator $\xi=3$.The results of the systematical bias
analysis are tabulated in table 1.
